Copulas and their potential for ecology

### 2019-09-12 Paper.Rmd
continued work on Background

Next intro tail dependence

<!--***DANr: Add a new section called Background on copulas.
It can have the following kinds of stuff (probably not exhaustive, and probably
not in order, and some of this material is currently below):
1) DONE - The definition, Sklar's theorem
2) DONE What good are copulas - intuitive idea, basically, but also have to be linked to 
the formalities of the definition
3) DONE What some of the different copula families look like - in particular you will use BB1 in Fig S2 and cite Background, so mention it
  Three new figures: Normal, Clayton, BB1
4) What tail dependence actually is

The explanation of how ranks relate to copulas and estimating the copula parameters
How to carry out fitting (basically, MLE fitting on ranks - Genest et al paper)

You are going to have to rearrange the order of some figs in Sup Mat because now the data section comes after Bacground, in which the different copula famlies are introduced
-->

>>>>

Having introduced tail dependence in a conceptual way and referred conceptually to it
in examples, we now need a more precise definition. 
<!--***DAN: fill in-->

Plots using normalized ranks were proposed in the Introduction as being conceptually
similar to copulas. We here explain the connection. As stated above, the copula associated
with a random variable $(X,Y)$ is the joint distribution function of the random variable
$(F_X(X),F_Y(Y))$. Given a sample $(x_i,y_i)$, $i=1,\ldots,n$, from $(X,Y)$, let $\hat{F}_X$ and
$\hat{F}_Y$ be the empirical cdfs associated with the $x_i$ and $y_i$, respectively.
These are step functions of $x$ and $y$, respectively, that start at $0$ for low values of 
$x$ and $y$ and jump by $1/n$
at each of the data points; for large $n$ they approximate the cdfs $F_X$ and $F_Y$. 
But $\hat{F}_X(x_i)$ equals the normalized rank of $x_i$ times
$n/(n+1)$, and likewise $\hat{F}_Y(y_i)$ equals the normalized rank of $y_i$ times
$n/(n+1)$. So the normalized rank in turn approximates the empirical cdf and therefore 
the cdf. Thus the normalized rank pairs $(u_i,v_i)$ for $i=1,\ldots,n$ can be 
regarded, for large $n$, as a sample from the bivariate pdf associated with the copula of $(X,Y)$,
and the scatterplot of $v_i$ versus $u_i$ can be used to infer aspects of copula structure
(see section on methods for Q1 below).

<!--***DANr: Add a new section called Background on copulas.
It can have the following kinds of stuff (probably not exhaustive, and probably
not in order, and some of this material is currently below):
1) DONE - The definition, Sklar's theorem
2) DONE What good are copulas - intuitive idea, basically, but also have to be linked to 
the formalities of the definition
3) DONE What some of the different copula families look like - in particular you will use BB1 in Fig S2 and cite Background, so mention it
  Three new figures: Normal, Clayton, BB1
STILL HAVE TO DO 4) What tail dependence actually is
DONE 5) The explanation of how ranks relate to copulas and estimating the copula parameters
How to carry out fitting (basically, MLE fitting on ranks - Genest et al paper)
-->

<!--***DAN:
You are going to have to rearrange the order of some figs in Sup Mat because now the data section comes after Bacground, in which the different copula famlies are introduced
-->
